An Innovative Storage Stack Addressing the Requirements of Extreme Scale Platforms and Big Data Applications

### 2014-04-17 paper.tex
Adding description of ACG and HDF5 layer
Fixed display of the author list and edited abstract

\title{An Innovative Storage Stack Addressing the Requirements of Extreme Scale Platforms}

\author{
\IEEEauthorblockN{Jay Lofstead}
\IEEEauthorblockA{Sandia National Laboratories\\gflofst@sandia.gov}
\and
\IEEEauthorblockN{Ivo Jimenez}
\IEEEauthorblockA{University of California, Santa Cruz\\ivo@cs.ucsc.edu}
\and
\IEEEauthorblockN{Carlos Maltzahn}
\IEEEauthorblockA{University of California, Santa Cruz\\carlosm@soe.ucsc.edu}
\and
\IEEEauthorblockN{Quincey Koziol}
\IEEEauthorblockA{HDF Group\\koziol@hdfgroup.org}
\and
\IEEEauthorblockN{John Bent}
\IEEEauthorblockA{EMC\\john.bent@emc.com}
\and
\IEEEauthorblockN{Eric Barton}
\IEEEauthorblockA{Intel\\eric.barton@intel.com}
}
\maketitle

@@

>>>>

\title{An Innovative Storage Stack Addressing the Requirements of Extreme Scale Platforms and Big Data Applications}

\author{
\IEEEauthorblockN{Jay Lofstead\IEEEauthorrefmark{1}, Ivo Jimenez\IEEEauthorrefmark{2}, Carlos Maltzahn\IEEEauthorrefmark{2}, Quincey Koziol\IEEEauthorrefmark{3}, John Bent\IEEEauthorrefmark{4}, Eric Barton\IEEEauthorrefmark{5}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Sandia National Laboratories gflofst@sandia.gov}
\IEEEauthorblockA{\IEEEauthorrefmark{2}University of California, Santa Cruz ivo@cs.ucsc.edu, carlosm@soe.ucsc.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}HDF Group koziol@hdfgroup.org}
\IEEEauthorblockA{\IEEEauthorrefmark{4}EMC john.bent@emc.com}
\IEEEauthorblockA{\IEEEauthorrefmark{5}Intel eric.barton@intel.com}
}
\maketitle

@@

In addition to these features supporting HPC platforms, the stack also addresses
the need of big data applications as demonstrated through the Arbitrary Connected Graphs tool.
